An efficient algorithm for integer lattice reduction

### 2023-06-21 tex/paper.tex
describing the random number generator

The implementation of the LLL algorithm of~\cite{lenstra-lenstra-lovasz}
used here is entirely in IEEE standard double-precision arithmetic,
with acceleration via basic linear algebra subroutines (BLAS)
and enhanced accuracy via re-orthogonalization.
BLAS originates from~\cite{lawson-hanson-kincaid-krogh},
\cite{blas}, and others, with implementation in Apple's Accelerate Framework
of Xcode for MacOS Ventura 13.2 in the experiments reported here
(and compiled using Clang LLVM with the highest optimization flag,
{\tt -O3}, set). All experiments ran on a 2020 MacBook Pro
with a 2.3~GHz quad-core Intel Core i7 processor
and 3.733~GHz LPDDR4X SDRAM.

>>>>

The implementation of the LLL algorithm of~\cite{lenstra-lenstra-lovasz}
used here is entirely in IEEE standard double-precision arithmetic,
with acceleration via basic linear algebra subroutines (BLAS)
and enhanced accuracy via re-orthogonalization.
BLAS originates from~\cite{lawson-hanson-kincaid-krogh},
\cite{blas}, and others, with implementation in Apple's Accelerate Framework
of Xcode for MacOS Ventura 13.4 in the experiments reported here
(and compiled using Clang LLVM with the highest optimization flag,
{\tt -O3}, set). All experiments ran on a 2020 MacBook Pro
with a 2.3~GHz quad-core Intel Core i7 processor
and 3.733~GHz LPDDR4X SDRAM.
For the greatest portability, the implementation calls {\tt random()}
to generate random numbers; many compiler distributions
implement {\tt random()} via the BSD linear-congruential generator
(such compilers include our implementation's defaults
of MacOS Clang referenced by {\tt gcc} under Xcode
and GNU {\tt gcc} under Linux).
